Reproducible research in archaeology using R & rrtools

### 2018-09-05 analysis/paper/paper.Rmd
oold stuff

---
title: "Reproducible research in archaeology using R & rrtools"
author:
  - Sophie C. Schmidt
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::html_document2:
      number_sections: false
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
---

@@

```{r, setup, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  cache = TRUE,
  comment = "#>",
  fig.path = "../figures/"
)

>>>>

---
title: "Reproducible research in archaeology using R & rrtools"
author:
  - Sophie C. Schmidt
  - Ben Marwick
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" 
---

@@

```{r, setup, echo = FALSE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  echo = TRUE,
  cache = TRUE,
  comment = "#>",
  fig.path = "../figures/"
)
